Prototype city generation for mobility simulation in urban typologies: a generalized framework

### 2017-12-27 manuscript/manuscript.tex
shell for framework diagram
tier diagram completed

@@

The population synthesis method that %\cite{petrik2016measuring}
used adapted ideas from probabilistic graphical models (PGM).
In their graphical model, there are 7 socio-demographic attributes, which are Age, Gender, Employment, Income, Car ownership, Purpose of trip, and Who pay for the trip, to represent a person.
Once the dependencies between variables are specified, we need to calculate or estimate conditional probability of one node given its parents.
The flexibility of this method is that those conditional probabilities can be derived from different sources like census data or surveys on individuals. Nevertheless, compared to the high dependency of IPF on the quality of sample data, Bayesian method gives synthetic population more heterogeneity.
Finally, the synthetic population is just random draws from the probabilistic graphical model.
Though we can take marginal distributions of all variables as supplement for the graphical model, the population generated by Bayesian network model can only precisely match the marginals of mother nodes.
This is because the distribution of a node is uniquely defined by its parent node and the conditional distribution based on PGM.
And this point should be taken into consideration when choosing the population synthesis method.

@@

\section{Method}

\begin{table}[h!]
  \centering
  \begin{tabular}{l l l}
    &&
  \end{tabular}
  \caption{List of symbols for variables and parameters}
  \label{tab:symbols}
\end{table}

@@

\subsection{Geolocation and spatial assignment}
\textcite{moekel2003microsimulation} present an intuitive approach to assigning households to zones, which we propose to implement.
First, they obtain land-use data, which they use to disaggregate zonal characteristics (e.g.\ household location or firm location) into raster cells.
The size of these cells are chosen based on computational tractability and desired resolution.
Weights are then assigned to the cells based on the corresponding land-use category.
For the household example, \textcite{moekel2003microsimulation} aggregate land-use attributes into the following: high-density housing, low-density housing, industry and open space;
to which weights of 10, 5, 1 and 1 are assigned, respectively.
The weights are then normalized by zone, and households are randomly selected to populate each cell to fit each proportion.
The address of each household is assumed to be the centroid of each cell, which each associated with its parent zone.
The rasterization is performed by a so-called ``point-in-polygon'' algorithm.
This approach presents a fast way for household assignment, assuming prior zonal assignment is available.
Our implementation is outlined in the following subsections.

@@

>>>>

%%%TIKZ
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{pgfgantt}
\pgfplotsset{compat=newest}

\usetikzlibrary{arrows,shapes,positioning,shapes.geometric}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{shadows,automata}
\usetikzlibrary{patterns}
\usetikzlibrary{trees,mindmap,backgrounds}
%\usetikzlibrary{circuits.ee.IEC}
\usetikzlibrary{decorations.text}
% For Sagnac Picture
\usetikzlibrary{%
    decorations.pathreplacing,%
    decorations.pathmorphing%
}
\tikzset{no shadows/.style={general shadow/.style=}}
%
%\usepackage{paralist}

@@

The population synthesis method that \citet{petrik2016measuring} used adapted ideas from probabilistic graphical models (PGM).
In their graphical model, there are 7 socio-demographic attributes, which are Age, Gender, Employment, Income, Car ownership, Purpose of trip, and Who pay for the trip, to represent a person.
Once the dependencies between variables are specified, we need to calculate or estimate conditional probability of one node given its parents.
The flexibility of this method is that those conditional probabilities can be derived from different sources like census data or surveys on individuals. Nevertheless, compared to the high dependency of IPF on the quality of sample data, Bayesian method gives synthetic population more heterogeneity.
Finally, the synthetic population is just random draws from the probabilistic graphical model.
Though we can take marginal distributions of all variables as supplement for the graphical model, the population generated by Bayesian network model can only precisely match the marginals of mother nodes.
This is because the distribution of a node is uniquely defined by its parent node and the conditional distribution based on PGM.
And this point should be taken into consideration when choosing the population synthesis method.

@@

\section{Method}
\begin{table}[h!]
  \centering
  \begin{tabular}{l l l}
    &&
  \end{tabular}
  \caption{List of symbols for variables and parameters}
  \label{tab:symbols}
\end{table}

@@

\begin{figure}[h!]
  \centering
  \begin{tikzpicture}[>=latex]
    \tikzset{tier/.style= {draw, rectangle, rounded corners, text width=25ex, align=center} }
    \tikzset{source/.style= {fill=gray!50!, rectangle,text width=15ex,font={\small}} }
    \tikzset{loca/.style= {draw,dotted, rectangle,text width=18ex,font={\small}} }
    \tikzset{head/.style= {draw=none,text width=18ex,font={\footnotesize\it}},align=center }

    \node[tier] (cell) at (0,0) {{\bf CELL}\\{\footnotesize via Rasterization}} ;
    \node[tier] (taz) [above= of cell] {{\bf TAZ}\\{\footnotesize Traffic Analysis Zone} } ;
    \node[tier] (sal) [above= of taz] {{\bf SAL} \\{\footnotesize Second Administrative Level}} ;
    \node[tier] (utp) [above= of sal] {{\bf UTP} \\{\footnotesize Urban Typology Prototype}} ;

    \node[head] (tier) [above= .5cm of utp] {Tier};
    \node[head] (source) [right= 1cm of tier] {Source};
    \node[head] (location) [right= 1cm of source] {Agent Location Resolution};

    \path[draw, ->] (utp) -- (sal);
    \path[draw, ->] (sal) -- (taz);
    \path[draw, ->] (taz) -- (cell);

    \node[source] (utp-source) [right= of utp] {Data};
    \node[source] (sal-source) [right= of sal] {Data};
    \node[source] (taz-source) [right= of taz] {Data/Generated};
    \node[source] (cell-source)[right= of cell]{Generated};

    \node[] (utp-location) [right= of utp-source] {};
    \node[] (sal-location) [right= of sal-source] {};
    \node[loca] (taz-location) [right= of taz-source] {Work (WORK), Education (EDU)};
    \node[loca] (cell-location)[right= of cell-source]{Household (HH)};
  \end{tikzpicture}
  \caption{The four tiers of the prototype city development framework. The UTP represents the urban typology, and is given by the metro area of the candidate city chosen for the supply.
  The Second Administrative Levels are the highest-level regions into which the UTP is subdivided. TAZ's are obtained for the UTP given the candidate road network. Where unavailable, these are generated as Thiessen polygons. CELLs are obtained by gridding over the SALs (or TAZs). The corresponding land use weight at the CELL level is used to determine the  {\it number} and {\it location} of the households therein; as well as the {\it numbers} of WORK and EDU points in each TAZ.}
  \label{fig:framework}
\end{figure}
\subsection{Geolocation and spatial assignment}
\textcite{moekel2003microsimulation} present an intuitive approach to assigning households to zones, which we propose to implement.
First, they obtain land-use data, which they use to disaggregate zonal characteristics (e.g.\ household location or firm location) into raster cells.
The size of these cells are chosen based on computational tractability and desired resolution.
Weights are then assigned to the cells based on the corresponding land-use category.
For the household example, \textcite{moekel2003microsimulation} aggregate land-use attributes into the following: high-density housing, low-density housing, industry and open space;
to which weights of 10, 5, 1 and 1 are assigned, respectively.
The weights are then normalized by zone, and households are randomly selected to populate each cell to fit each proportion.
The address of each household is assumed to be the centroid of each cell, which each associated with its parent zone.
The rasterization is performed by a so-called ``point-in-polygon'' algorithm.
This approach presents a fast way for household assignment, assuming prior zonal assignment is available.
Our implementation is outlined in the following subsections.

@@

\subsection{Calibration and validation}
Initially tune parameters.

\subsubsection{Trip structure}
Aggregate modeshares for the typology

\subsubsection{Activity structure}
Consider cities near supply-demand interaction centroid:
\begin{itemize}
\item Supply-demand interaction defined by factors, namely: congestion/highway domination and inefficiency
\item If travel surveys are available: validate against activity shares
\end{itemize}
